---
title: "Milestone-Report"
author: "Yigang"
date: "2021/4/2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction

The goal of this project is just to display that you've gotten used to working with the data and that you are on track to create your prediction algorithm. Please submit a report on R Pubs (http://rpubs.com/) that explains your exploratory analysis and your goals for the eventual app and algorithm. This document should be concise and explain only the major features of the data you have identified and briefly summarize your plans for creating the prediction algorithm and Shiny app in a way that would be understandable to a non-data scientist manager. You should make use of tables and plots to illustrate important summaries of the data set. The motivation for this project is to: 

1. Demonstrate that you've downloaded the data and have successfully loaded it in.
2. Create a basic report of summary statistics about the data sets.
3. Report any interesting findings that you amassed so far.
4. Get feedback on your plans for creating a prediction algorithm and Shiny app.  

Capstone Dataset: https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip

## Load Data
```{r}
library(NLP)
library(tm)
library(stringi)
library(dplyr)
library(RColorBrewer)
library(wordcloud)
library(SnowballC)
library(RWeka)
blogs <- readLines("final/en_US/en_US.blogs.txt", encoding = "UTF-8", skipNul = TRUE)
news <- readLines("final/en_US/en_US.news.txt", encoding = "UTF-8", skipNul = TRUE)
twitter <- readLines("final/en_US/en_US.twitter.txt", encoding = "UTF-8", skipNul = TRUE)

```

# Check data
```{r}
blogs.size <- file.info("final/en_US/en_US.blogs.txt")$size / 1024 ^ 2
news.size <- file.info("final/en_US/en_US.news.txt")$size / 1024 ^ 2
twitter.size <- file.info("final/en_US/en_US.twitter.txt")$size / 1024 ^ 2

data.frame("filename" = c("blogs", "news", "twitter"),
           "filesize.MB" = c(blogs.size, news.size, twitter.size),
           "num.lines" = c(length(blogs), length(news),length(twitter)),
           "num.words" = c(sum(stri_count_words(blogs)), 
                           sum(stri_count_words(news)), sum(stri_count_words(twitter))))
```

## Clean Data
```{r}
set.seed(1234)
twsample <- sample(twitter, length(twitter)*0.05 ) #take sample

twcorpus <- VCorpus(VectorSource(twsample)) %>% # convert to vector
        tm_map(., PlainTextDocument) %>% # create a plain text document
        tm_map(., content_transformer(tolower)) %>% # transform to lower case
        tm_map(., removePunctuation) %>% # remove punctuation
        tm_map(., removeNumbers)%>% # remove numbers
        tm_map(., stripWhitespace) %>% # remove extra white space
        tm_map(., function(x)iconv(x, "latin1", "ASCII", sub=""))%>% # remove all non-ASCII chars
        tm_map(., stemDocument) # apply Porter's stemming algorithm

```

### make word cloud
```{r}
# make word cloud
twcorpusx <- as.matrix(TermDocumentMatrix(twcorpus))
wordcloud(twcorpusx, max.words = 100, random.order = FALSE,
          colors=brewer.pal(8,"Accent"))
twcorpusz <- as.character(twcorpus)

```


# Tokenize sample into Unigrams, Bigrams and Trigrams
```{r}
unigram <- function(x) NGramTokenizer(x, Weka_control(min = 1, max = 1))
bigram <- function(x) NGramTokenizer(x, Weka_control(min = 2, max = 2))
trigram <- function(x) NGramTokenizer(x, Weka_control(min = 3, max = 3))

unigramx <- TermDocumentMatrix(twcorpus, control = list(tokenize = unigram))
bigramx <- TermDocumentMatrix(twcorpus, control = list(tokenize = bigram))
trigramx <- TermDocumentMatrix(twcorpus, control = list(tokenize = trigram))

freqTerms <- findFreqTerms(unigramx, lowfreq = 5000)
termFrequency <- rowSums(as.matrix(unigramx[freqTerms,]))
termFrequency <- data.frame(unigram=names(termFrequency), frequency=termFrequency)

g <- ggplot(termFrequency, aes(x=reorder(unigram, frequency), y=frequency)) +
        geom_bar(stat = "identity") + 
        coord_flip() +
        xlab("Unigram") + ylab("Frequency") +
        labs(title = "Top Unigrams by Frequency")
print(g)


```





